The \dealii Library, Version 9.7

### 2025-07-28 9.7/paper.tex
Complete outline.

While all of these major changes are discussed in detail in
Section~\ref{sec:major}, there
are a number of other noteworthy changes in the current \dealii release,
which we briefly outline in the remainder of this section:
%
\begin{itemize}
\item MPGMRES and GMRES updates
  \todo[inline]{Matthias and Martin, please update (or make this point
  into one or two subsections below).}
\item FiniteElement::shape\_function\_belongs\_to()
  \todo[inline]{Wolfgang to complete}
  \item \todo[inline]{Add to this list other points that are not
    explicitly discussed below}
\end{itemize}
%
The
\href{https://dealii.org/current/doxygen/deal.II/changes_between_9_6_0_and_9_7_0.html}{changelog}
-- listing more than 120
features and bugfixes --
contains a complete record of all changes; see \cite{changes97}.

@@

\todo[inline]{Perhaps say something about new interfaces to MUMPS and
  PSBLAS, and the updated interfaces to ArborX. We no longer bundle
  TBB and by default build on Taskflow. More interfaces to CGAL. Now
  bundling Kokkos 4.5.1; are we using something new from Kokkos? magic\_enum}

@@

  \item The 9.5 release~\cite{dealII95} made \kokkos~\cite{trott2022} a required
    dependency. Kokkos is a C++ library which provides tools for writing code
    which can efficiently run on a diverse set of architectures and devices.
    The current release removes the deprecated \texttt{CUDAWrappers} namespace as well
    as all \texttt{CUDA}-related macros in favor of Kokkos
    equivalents.
    \todo[inline]{Perhaps move to Section~\ref{subsec:external}?}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{How to cite \dealii}\label{sec:cite}

>>>>

While all of these major changes are discussed in detail in
Section~\ref{sec:major}, there
are a number of other noteworthy changes in the current \dealii release,
which we briefly outline in the remainder of this section:
%
\begin{itemize}
\item MPGMRES and GMRES updates
  \todo[inline]{Matthias and Martin, please update (or make this point
  into one or two subsections in Section 2 below).}
\item A common operation in the finite element codes is to ask whether
  a specific shape function belongs to a particular solution
  variable. In the past, this was implemented by using the
  \texttt{FiniteElement::system\_to\_component\_index()} function that
  returns, among other information, which vector component a shape
  function belongs to. One then had to test whether this is the vector
  component (or one of the vector components) that corresponds to a
  specific variable. The new
  \texttt{FiniteElement::shape\_function\_belongs\_to()} makes this
  easier: It takes as argument a \texttt{FiniteElementExtractor} that
  corresponds to a scalar, vector-valued, or tensor-valued set of
  solution variables, and directly returns \texttt{true} or
  \texttt{false}.
\item \todo[inline]{Perhaps mention the updated interfaces to ArborX
  here? (Or in Section~\ref{subsec:external}?)}
\item \todo[inline]{Add to this list other points that are not
    explicitly discussed below}
\end{itemize}
%
The
\href{https://dealii.org/current/doxygen/deal.II/changes_between_9_6_0_and_9_7_0.html}{changelog}
-- listing more than 120
features and bugfixes --
contains a complete record of all changes; see \cite{changes97}.

@@

\dealii{} relies on external software packages for many operations
that are not within the core functionality of a finite element package
-- see Section~\ref{sec:cite} for a complete list. As in every
release, we have continued to expand and revise these interfaces. The
following sub-sections outline these updates.

\subsubsection{Interfaces to the Threading Building Blocks and to
  Taskflow}

\todo[inline]{There is text about this elsewhere in this
  document. Perhaps move here?}
\cite{huang2021taskflow}
\cite{reinders2007tbb}

\subsubsection{Kokkos, a performance portability library}
\label{subsec:external-kokkos}

Kokkos is a C++ library that makes it easy to write codes that can
portably run on CPUs and GPUs of different vendors, using their
respectiv underlying programming models.
The \dealii{} 9.5 release~\cite{dealII95} made \kokkos~\cite{trott2022} a required
dependency. The current release removes the deprecated \texttt{CUDAWrappers} namespace as well
as all \texttt{CUDA}-related macros in favor of Kokkos
equivalents.

\todo[inline]{Now
  bundling Kokkos 4.5.1; are we using something new from Kokkos? magic\_enum}

\subsubsection{MUMPS, a multifrontal parallel direct solver}

\todo[inline]{Luca, want to say something here? If not, please delete
  the subsubsection.}

\subsubsection{PSBLAS, a XXXXX}

\todo[inline]{Complete section name}

\todo[inline]{Luca, want to say something here? If not, please delete
  the subsubsection.}

\subsubsection{\texttt{magic\_enum}, a XXXXX}

\todo[inline]{Complete section name}
\todo[inline]{Luca, want to say something here? If not, please delete
  the subsubsection.}

\subsubsection{CGAL, a computational geometry engine}

\todo[inline]{Do we want to say something here? If not, please delete
  the subsubsection.}

@@

  \item As already mentioned in
    Section~\ref{subsec:external-kokkos}, the current release
    removes the deprecated \texttt{CUDAWrappers} namespace as well 
    as all \texttt{CUDA}-related macros in favor of Kokkos
    equivalents.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{How to cite \dealii}
\label{sec:cite}
